High Performance Computing Project\\ Parallelization of the Probabilistic Roadmap Method with GPU Acceleration

### 2016-06-01 paper/presentation.tex
presentation

%%%%%%%%%%%%%%%%%%%%%%%
%\section{Motivation}
\begin{frame}
\frametitle{Motivation}
	\begin{center}
		\includegraphics[height=4cm]{configspacetrafo.png}
	\end{center}
	\begin{itemize}
		\item Problem: find a feasible trajectory of a robot through a setting of obstacles
		\item often necessary to pass feasible initial tajectories to optimization algorithms
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Problem Statement}
	\begin{itemize}
		\item Obstacles can not be assumed to have a closed form
		\item Therefore they are defined by an indicator function
		\begin{equation*}
			I: \Omega \subset \R^d \rightarrow \{ 0,1 \}
		\end{equation*}
		\item collision for $q \in \Omega$, $I(q) = 1$ 
	\end{itemize}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%
%\section{Motivation}
\begin{frame}
\frametitle{Motivation}
	\begin{center}
		\includegraphics[height=4cm]{configspacetrafo.png}
	\end{center}
	\begin{itemize}
		\item Problem: find a feasible trajectory of a robot through a setting of obstacles
		\item Often necessary to pass feasible initial tajectories to optimization algorithms
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Problem Statement}
	\begin{itemize}
		\item Obstacles can not be assumed to have a closed form
		\item Therefore they are defined by an indicator function
		\begin{equation*}
			I: \Omega \subset \R^d \rightarrow \{ 0,1 \}
		\end{equation*}
		\item Collision for $q \in \Omega$, $I(q) = 1$ 
	\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{Indicator Function Implementation}
\begin{itemize}
	\item Input: vectors of start and end nodes for each potential edge
	\item Output: vector of feasible edges
	\item CPU determines number of threads needed for each edge
		 and passes nodes to GPU 
	\item Each CUDA thread determines his intermediate configuration and checks for collsion
	\begin{itemize}
		\item Kinematics with Denavit-Hartenberg transformations
		\item Geometry parts are convex polytopes
		\item Collision detection: Chung-Wang Collision Algorithm
	\end{itemize}
\end{itemize}
\end{frame}
